{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-08-03 documents/pamphlet.tex
Noweb -> pweave
Minted garbage
SA test
Yay LO working, except we don't need it anymore

This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}

Both the microwave and microbiology components of this field\footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}. Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.

This project was rushed and slow, terribly managed, and not nearly as rigorous as the field demands. This may well end up being a waste of time.

@@

@@

If the above is correct, any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 100 ns will be sterilized. (TODO field strength)

@@

First, depending on the type of tissue, this field strength can apparently be safely produced a minimum of 3 cm deep (suitable for targeted sterilization of lungs or other organs with bronchoscopic techniques), up to 200 cm (eradicating the virus from the body) \cite{Physical1982}. We are working to narrow these bounds now.

@@

Unlike UV, the X-band is minimally attenuated by air. Common areas could be illuminated by magnetron systems.

On the other extreme, installations with megawatt-scale klystrons could sterilize square-kilometer areas at a time.

{\Large \textbf{Tasks}}

We can see the following

\begin{itemize}
	\item To prevent duplication of work, are any other teams working on this now? It seems a rather obvious technique. A thorough review of arxiv etc should be performed.
	\item Double-check all figures and assumptions.
	\item Send off spectrometer (or, ideally, a more precise piece of equipment) to a BSL with a sample of NCoV to obtain the spectra and thresholds.
	\item get the gosh-darned AustinMan voxel team to reply to my gosh-darned emails
	\item Determine the ideal application to focus effort on
	\item ???????
	\item Check with the FCC/Industry Canada if we can get a temporary exemption for these intentional radiators?

\end{itemize}

>>>>

This is a condensed version of a (horribly unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Daniel Correia [TODO: affiliation] \orcidlink{0000-0002-9353-0216}}

%\subfile{pulse_1.tex}

Both the microwave and microbiology components of this field appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}. Though the cited articles have taken care to avoid these effects, it is entirely possible that none of what is discussed below actually exists.

Please distrust our analysis.

@@

\begin{autem}
	It should be noted that all of the claims we make hinge on this nanosecond inactivation. \cite{Efficient2015} and \cite{focusing2014} use a 15-minute exposure, which is apparently the norm for this field. 
\end{autem}

{\Large \textbf{Advantages over existing techniques}}

From crude attenuation data, this pulsed field can be safely produced at least 3 cm deep in tissue. This would seem to be unlike any other mechanisms like near or far\cite{Germicidal2017}UV. suitable for targeted sterilization of with bronchoscopic techniques), opening up a particularly interesting direct treatment modality. We are trying to verify this now with FDTD sims.

Also unlike UV, the X-band is minimally attenuated by air; in the extreme, installations with megawatt-scale klystrons could potentially prevent airborne transmission in square-kilometer areas.

@@

@@

@@
